Carbonate chemistry at Ny-Ålesund

### 2021-03-04 awipev-CO2.Rmd
Finalized time series plot

#################### Mytheme
Mytheme <- function(size_labs = 7, face_font="plain") {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
        aspect.ratio = 1 / 2,
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
  )
}

@@

# pH seaFET Final
# add despike with n=2 k = 5762 to the final ph corrected data
# despike me semble inutile, faire plutôt un simple des outliers qui, vérification faite, n'est même pas nécessaire
# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_9m for consistency with salinity and temp
d_all <- d_all %>%
  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
  dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
  dplyr::mutate(pHint_tot_sf_1m = ifelse(pressure_insitu_ctd > 0 & pressure_insitu_ctd < 2, pHint_tot_sf, NA),
                pHint_tot_sf_3m = ifelse(pressure_insitu_ctd >= 2 & pressure_insitu_ctd < 4, pHint_tot_sf, NA),
                pHint_tot_sf_5m = ifelse(pressure_insitu_ctd >= 4 & pressure_insitu_ctd < 6, pHint_tot_sf, NA),
                pHint_tot_sf_7m = ifelse(pressure_insitu_ctd >= 6 & pressure_insitu_ctd < 8, pHint_tot_sf, NA),
                pHint_tot_sf_9m = ifelse(pressure_insitu_ctd >= 8 , pHint_tot_sf, NA)
  )

@@

p <- cowplot::plot_grid(p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m, ncol = 1)
pngfile <- "figures/air-sea_CO2_flux.png"
ggsave(
  pngfile, 
  p, 
  device = agg_png, 
  width = 6.6, height = 10, units = "cm", res = 300,
  scaling = 0.4
)
knitr::include_graphics(pngfile)
```

@@

```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
size_point <- 2 # size of data points
alpha <- 1 #transparency

d <- d_all %>% 
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  tsibble::fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
#  dplyr::rename(pco2_contros = pco2_corr) %>% 
  replace(., is.na(.), NA) # replace NaN by NA everywhere

d_ts <- d %>%
  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_fb,
                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
  #tidyr::pivot_longer(-datetime, values_to = "value")

#sal_fb
ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Salinity FerryBox",x="", y="Salinity") +
  Mytheme(size_labs = 8)
# ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
# filename.html <- paste0(path_fig, "ts_sal_py.html")
# saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")

# temp_insitu_11m
ts_temp <- d_all %>%
  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
  Mytheme(size_labs = 8)

# PAR
ts_par_air <- d_all %>%
  ggplot(aes(x = datetime, y = par_air), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
  Mytheme(size_labs = 8)

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_fb), 
             colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
  Mytheme(size_labs = 8)

# SEAFET pH
ts_pH <- d_all %>%
  ggplot(aes(x = datetime, y = pHint_tot_sf_9m), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="In situ pH below 8 m (seaFET in blue, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = 8)

# AT
ts_at <- d_all %>%
  ggplot(aes(x = datetime, y = at_calc), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = at), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
  Mytheme(size_labs = 8)

# Combine plots
g <- (ts_sal / ts_temp / ts_par_air / ts_pCO2 / ts_pH / ts_at)
g <- g + plot_annotation(tag_levels = 'A')
g

g <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
print(g)
```
## Maintenance
<div style="text-align: justify">

>>>>

#################### Mytheme
Mytheme <- function(size_labs = 7, face_font="plain") {
  theme_bw() +
  theme(title = element_text(face=face_font, size=size_labs, color="black"),
        legend.title = element_text(face=face_font, size=size_labs, color="black"),
        legend.text = element_text(face=face_font, size=size_labs, color="black"),
        axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
        #aspect.ratio = 1 / 2,
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
  )
}

@@

# pH seaFET Final
# add despike with n=2 k = 5762 to the final ph corrected data
# despike me semble inutile, faire plutôt un simple des outliers qui, vérification faite, n'est même pas nécessaire
# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_9m for consistency with salinity and temp
d_all <- d_all %>%
  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
  dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
  dplyr::mutate(pHint_tot_sf_1m = ifelse(pressure_insitu_ctd > 0 & pressure_insitu_ctd < 2, pHint_tot_sf, NA),
                pHint_tot_sf_3m = ifelse(pressure_insitu_ctd >= 2 & pressure_insitu_ctd < 4, pHint_tot_sf, NA),
                pHint_tot_sf_5m = ifelse(pressure_insitu_ctd >= 4 & pressure_insitu_ctd < 6, pHint_tot_sf, NA),
                pHint_tot_sf_7m = ifelse(pressure_insitu_ctd >= 6 & pressure_insitu_ctd < 8, pHint_tot_sf, NA),
                pHint_tot_sf_9m = ifelse(pressure_insitu_ctd >= 8 , pHint_tot_sf, NA),
                depth_discrete = case_when(
      !is.na(pHint_tot_sf_1m) ~ 1,
      !is.na(pHint_tot_sf_3m) ~ 3,
      !is.na(pHint_tot_sf_5m) ~ 5,
      !is.na(pHint_tot_sf_7m) ~ 7,
      !is.na(pHint_tot_sf_9m) ~ 9
      ),
      depth_discrete = as.factor(depth_discrete)
  )

@@

p <- cowplot::plot_grid(p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m, ncol = 1)
pngfile <- "figures/air-sea_CO2_flux.png"
ggsave(
  pngfile, 
  p, 
  device = agg_png, 
  width = 6.6, height = 10, units = "cm", res = 300,
  scaling = 0.4
)
rm(p_f_air_sea)
knitr::include_graphics(pngfile)
```

@@

```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
size_point <- 0.3 # size of data points
alpha <- 1 #transparency
size_labs <- 6 # font size labels

ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Salinity FerryBox",x="", y="Salinity") +
  Mytheme(size_labs = size_labs)

# temp_insitu_11m
ts_temp <- d_all %>%
  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
  Mytheme(size_labs = size_labs)

# PAR
ts_par_air <- d_all %>%
  ggplot(aes(x = datetime, y = par_air), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
  Mytheme(size_labs = size_labs)

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_fb), 
             colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
  labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
  Mytheme(size_labs = size_labs)

# SEAFET pH
ts_pH <- d_all %>% 
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pHint_tot_sf, col = pressure_insitu_ctd), alpha=alpha, na.rm=TRUE, size=size_point) + 
  scale_colour_gradient(name = "Depth (m)", low = "#56B1F7", high = "#132B43") + # reverse colors
  guides(colour = guide_colourbar(reverse = TRUE)) + # reverse colour bar
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
  labs(title="In situ pH, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = size_labs) +
  theme(legend.position = c(0.1, 0.5),
        legend.key.height = unit(0.5, 'cm'))

# AT
ts_at <- d_all %>%
  ggplot(aes(x = datetime, y = at_calc), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = at), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
  labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
  Mytheme(size_labs = size_labs)

# Combine plots
g <- (ts_sal / ts_temp / ts_par_air / ts_pCO2 / ts_pH / ts_at)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
#rm(ls(pattern = "ts_"))

#save_plot(filename = "figures/time_series.png", plot = g)
#g_cw <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
```
## Maintenance
<div style="text-align: justify">
